<!--
%\VignetteEngine{knitr}
%\VignetteIndexEntry{HWxtest}
-->
```{r setup, include=FALSE}
library(knitr)
library(knitcitations)
opts_chunk$set(fig.width=8, fig.height=5)
set.seed(60823316) 
```
```{r refs, include=FALSE}
# bib <- read.bibtex('~/DropBox/HWxtest/bibHW.txt')
bib <- read.bibtex('../inst/bibHW.txt')
me2009 <- ref("10.1534/genetics.109.108977")
levene1949 <- ref("10.1214/aoms/1177730093")
haldane1954 <- ref("10.1007/BF02985085")
louis1987 <- ref("10.2307/2531534")
guo1992 <- ref("10.2307/2532296")
ward2014 <- ref("10.1093/biostatistics/kxt028")
rousset1995 <- bib[["R1995"]]
robertson1984 <- bib[["robertson1984"]]
genepop007 <- bib[["genepop007"]]
```


<STYLE type="text/css">
  h1,h2,h3,h4,h5 { 
    font-family: palatino, georgia, serif;
    color: Maroon;
  }
    h1, h6{
    text-align: center;
  }
  h1{line-height: 50px}
  body{
    font-size: 0.9em;
    line-height: 23px;
  }
  h3{
  font-weight: normal;
  }
  h6{
        font-size: 0.9em;
        font-weight: normal;
        line-height: 5px;      
   }
   hr{
     border-top-style: solid;
     border-top-width: medium;
   }
  code {
    font-size: 80%;
    line-height: 140%;
    border: 1px solid #ccc;
  }
   @media print{
  hr { 
      visibility: inherit;
      page-break-before: auto;
    }
   }
 </STYLE>


* * *
HWxtest -- Exact Tests for Hardy-Weinberg Proportions With Multiple Alleles
========================================================

###### William R. Engels  <wrengels@wisc.edu>  
###### University of Wisconsin, Madison -- Genetics Department
* * *
### Contents
* Introduction -- [1](#intro)
* Bibliography -- [2](#bib)
```{r}
getwd()
```

### <a name="intro">Introduction</a>
This packages uses algorithms from `r citep(me2009)` for everything.See also `r citep(list(levene1949, haldane1954, guo1992, louis1987, ward2014, rousset1995, genepop007))` for good stuff `r citet(c(rousset1995, robertson1984))`.

### More stuff

### More yet

### <a name="bib">Bibliography</a>
```{r results="asis", echo=FALSE}
bibliography("html")
````